Hybrid platforms and bargaining power

### 2023-03-25 src/paper/application.tex
Even more figures in the model section

                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .9, .1) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are complements}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {x^0.5};
                \node[anchor=north west] at (axis cs: .6, .6^0.5) {$\tilde{f}(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .1, .9) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .9, .1) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are substitutes}
    \end{subfigure}
    \caption{Distribution of value between the platform and the fringe (with $w(s) \equiv 1$)}
    \label{fig:outcome_based_bargaining_power}
\end{figure}

@@

                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $f$}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {ln(1+x)};
                \addplot[name path=tildef, blue,ultra thick] {x};
                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$\tilde{f}(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $\tilde{f}$}
    \end{subfigure}
    \caption{Illustration of \cref{prop:share_of_platform}}
    \label{fig:increase_N_P_platform}
\end{figure}

Next, let us look at an analogous result for the fringe firms.
As the next proposition demonstrates, in this case, the direction of the change depends on the complementarities between the fringe firms.
\begin{proposition}
    \label{prop:share_of_fringe}
    Assume that $f, w$ are twice continuously differentiable and that $w$ has a non-zero measure support.
    Let $N_F > 0$.
    Then $\pi_F$ is also differentiable.
    \begin{align*}
        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
        &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
    \end{align*}
    for all $N_P \geq 0$.
\end{proposition}
In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms.
On the other hand, when the fringe firms are mostly complements the fringe's profits increase.

>>>>

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are complements}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {x^0.5};
                \node[anchor=north west] at (axis cs: .6, .6^0.5) {$\tilde{f}(N_P, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \path[name path=top] (axis cs:0,1) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Fringe firms are substitutes}
    \end{subfigure}
    \caption{Distribution of value between the platform and the fringe (with $w(s) \equiv 1$)}
    \label{fig:outcome_based_bargaining_power}
\end{figure}

@@

                \node[anchor=north west] at (axis cs: .05, .65) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P$}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {ln(1+x)};
                \addplot[name path=tildef, blue,ultra thick] {x};
                \node[anchor=south east] at (axis cs: 0.6, 0.6) {$f(N_P', sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

@@

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P'$}
    \end{subfigure}
    \caption{Illustration of \cref{prop:share_of_platform} ($N_P < N_P'$)}
    \label{fig:increase_N_P_platform}
\end{figure}

Next, let us look at an analogous result for the fringe firms.
As the next proposition demonstrates, in this case, the direction of the change depends on the complementarities between the fringe firms.
\begin{proposition}
    \label{prop:share_of_fringe}
    Assume that $f, w$ are twice continuously differentiable and that $w$ has a non-zero measure support.
    Let $N_F > 0$.
    Then $\pi_F$ is also differentiable.
    \begin{align*}
        &\text{If } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} < 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} < 0, \\
        &\text{if } \frac{\partial^2 f(N_P, n_F)}{\partial n_P \partial n_F} > 0 \;\forall n_F \leq N_F, \text{ then } \frac{\partial \pi_F(N_P, N_F)}{\partial N_P} > 0
    \end{align*}
    for all $N_P \geq 0$.
\end{proposition}
In summary, when they are mostly substitutes (the cross-derivatives of $f$ are negative), the fringe's profits decrease as a result of an increase in $N_F$.
The intuition is that, even though the total size of the pie increases, the bargaining power of the fringe deteriorates so much that its share decreases not only in relative, but also in absolute terms (as illustrated in \cref{fig:increase_N_P_fringe}).
On the other hand, when the fringe firms are mostly complements the fringe's profits increase.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, blue,ultra thick] {sqrt(x)};
                \addplot[name path=tildef, dashed, black] {sqrt(0.5+x)};
                \node[anchor=north west] at (axis cs: .6, 0.77) {$f(0, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1) -- (axis cs:1,1);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1);

                \node[anchor=north west] at (axis cs: .05, .95) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P = 0$}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}[scale=0.8]
            \begin{axis}[xmin=0, xmax=1, ymin=0, ymax=1.225, samples at={0, 0.02, ..., 0.98, 1},
                xtick={0, 1}, ytick={0}, axis lines=left, xlabel={$s$}]
                \addplot[name path=f, dashed, black] {sqrt(x)};
                \addplot[name path=tildef, blue,ultra thick] {sqrt(0.5+x)};
                \node[anchor=north west] at (axis cs: 0, 0.7) {$f(0.5, sN_F)$};
                \path[name path=bottom] (axis cs:0,0) -- (axis cs:1,0);
                \draw[name path=top] (axis cs:0,1.225) -- (axis cs:1,1.225);
                \draw[name path=right] (axis cs:1,0) -- (axis cs:1,1.225);

                \node[anchor=north west] at (axis cs: .05, 1.17) {Fringe ($A$)};
                \node[anchor=south east] at (axis cs: .95, .05) {Platform ($P$)};
            \end{axis}
        \end{tikzpicture}
        \caption{Profit shares with $N_P = 0.5$}
    \end{subfigure}
    \caption{Illustration of \cref{prop:share_of_fringe} (fringe firms are substitutes, $f(N_P, N_F) = \sqrt{N_P + N_F}$)}
    \label{fig:increase_N_P_fringe}
\end{figure}
